Towards human SuperEEG

### 2018-10-05 paper/main.tex
backing up changes (working on results; WIP)

The SuperEEG algorithm described above and in
Figure~\ref{fig:methods} allows us to estimate (up to a constant
scaling factor) LFPs for each patient at all arbitrarily chosen
locations in the set $\bar{R}$, \textit{even if we did not record that
  patient's brain at all of those locations}.  We next turn to an
evaluation of the accuracy of those estimates.

@@

\textbf{JRM STOPPED HERE}
% JRM thoughts:
% - Do we need to use the term "LFP"?
% - Tie in stats from supplemental analyses.  Fig S4: total number of
% electrodes, total number of used electrodes, prop thresholded, total
% recording time, average session time, number of sessions.

We first examined raw LFP traces and their associated SuperEEG-derived
reconstructions.  Figure~\ref{fig:recon}A displays the LFP from the
red electrode in Figure~\ref{fig:methods}A, and its associated
reconstruction, during a 5~s time window during one of the patient's 6
recording sessions.  Figure~\ref{fig:recon}B displays a 2D histogram
of the observed versus reconstructed voltages for every sample across
14.2 total hours of recordings from that patient (correlation:
$r = 0.91, p < 10\textsuperscript{-10}$).  Although the SuperEEG
algorithm recovered the recordings from this electrode well, we sought
to quantify the algorithm's performance across the full dataset.

>>>>

The SuperEEG algorithm described above and in Figure~\ref{fig:methods}
allows us to estimate, up to a constant scaling factor, local field
potentials (LFPs) for each patient at all arbitrarily chosen locations
in the set $\bar{R}$, \textit{even if we did not record that patient's
  brain at all of those locations}.  We next turn to an evaluation of
the accuracy of those estimates.

@@

We first examined held-out raw LFP traces and their associated
SuperEEG-derived reconstructions.  Figure~\ref{fig:recon}A displays
the observed LFP from the red electrode in Figure~\ref{fig:methods}A
(red), and its associated reconstruction (black), during a 5~s time
window during one of the example patient's six recording sessions.
The two traces match closely ($r = XXX, p = XXX$).  Where the traces
do not align, the predicted trace tends to be rounded towards zero,
reflecting the zero-mean prior implicit in
Equation~\ref{eqn:reconstruction} (paired $t$-test comparing absolute
values of actual versus predicted voltages: $t(XXX) = XXX, p = XXX$).

\textbf{JRM STOPPED HERE}
% JRM thoughts:
% - Tie in stats from supplemental analyses.  Fig S4: total number of
% electrodes, total number of used electrodes, prop thresholded, total
% recording time, average session time, number of sessions.

Figure~\ref{fig:recon}B displays a two-dimensional histogram of the
actual versus reconstructed voltages for every sample across 14.2
total hours of recordings from that patient (correlation:
$r = 0.91, p < 10\textsuperscript{-10}$).  Although the SuperEEG
algorithm recovered the recordings from this electrode well, we sought
to quantify the algorithm's performance across the full dataset.
